---
title: "R Notebook"
output: html_notebook
---

```{r}
#install packages
if (!require("pacman")) install.packages("pacman")
require("pacman", character.only = TRUE, quietly = TRUE)
p_load(tidyverse, GA, pso,Rcpp, BPSO, tabuSearch)
p_load(randomForest, xgboost, glmnet, AUC, e1071, FNN, fastAdaboost, lightgbm, rotationForest)
# install.packages("remotes")
# remotes::install_github("DominikMueller64/BPSO")
```

```{r}
# Select team, year and race type
# Our case is about optimal team selection of Jumbo-Visma in 2021 in flat races.
team = 'Jumbo-Visma'
year = 2021
race_category = 'Flat' 
```

```{r}
# Get the whole available team in a given year
team_all <- basetable %>% filter((Team.x == team) & (Year == year)) %>% distinct(Rider,.keep_all = T) %>% select(Rider,Team.x) # Select the available team members of a given team in a given year

# Team size is used later on in GA algorithm
team_size_all <- nrow(team_all)
```

```{r}
team_all
```
```{r}
#Possibly good solution: 
good_initial <- c(0,0,0,0,1,0,0,1,1,0,0,0,0,0,0,0,1,0,1,0,1,0,0,1)
good_initial <- t(as.matrix(good_initial))
```

```{r}
team_selection <- c(0,0,0,0,1,0,0,1,1,0,0,0,0,0,0,0,1,0,1,0,1,0,0,1)
team_selection
```

```{r}
team_selection_name <- team_all[team_selection == 1,'Rider'] # Get names of selected riders
team_selection_base <- basetable %>% distinct(Rider,.keep_all = T) %>% filter(Rider %in% team_selection_name)
team_selection_name
```

```{r}
# Summarize function to make the same basetable the models were trained on 
summarize_function <- function(team_selection, race_category){
  team_selection_name <- team_all[team_selection == 1,'Rider'] # Get names of selected riders
  
  team_selection_base <- basetable %>% distinct(Rider ,.keep_all = T) %>% filter(Rider %in% team_selection_name$Rider) %>% ungroup() # Get information on the selected riders. The columns which we summarize in the next step are static. So it doesn't matter which race we get the riders information from. 

  # Calculate team scores
  team <- team_selection_base %>%
    summarise( team_popularity = sum(Popularity), team_potential = sum(Potential),
            team_score_flat = sum(FLAT), team_score_mountain = sum(MOUNTAIN), team_score_downhill = sum(DOWNHILL),
            team_score_cobbles = sum(COBBLES), team_score_tt = sum(TT), team_score_prologue = sum(PROLOGUE),
            team_score_sprint = sum(SPRINT), team_score_acceleration = sum(ACCELERATION), team_score_endurance = sum(ENDURANCE),
            team_score_resistance = sum(RESISTANCE), team_score_recup = sum(RECUP), team_score_hill = sum(HILL),
            team_score_attack = sum(ATTACK), 
            avg_team_size = mean(Size), avg_team_weight = mean(Weight),
            nr_drivers = n_distinct(Rider),
            nr_flat_drivers = sum(flat_driver), nr_mountain_drivers = sum(mountain_driver), nr_downhill_drivers = sum(downhill_driver),
            nr_cobbles_drivers = sum(cobbles_driver), nr_tt_drivers = sum(tt_driver), nr_prologue_drivers = sum(prologue_driver),
            nr_sprint_drivers = sum(sprint_driver), nr_acceleration_drivers = sum(acceleration_driver), nr_resistance_drivers =
              sum(resistance_driver), nr_endurance_drivers = sum(endurance_driver), nr_recup_drivers = sum(recup_driver), 
            nr_hill_drivers = sum(hill_driver), nr_attack_drivers = sum(attack_driver), avg_age_drivers = mean(age))

  
  # add race category as numeric to team
  team[colnames(dummies)] <- as.numeric(1)
  category <- race_category
  category <- paste('Race_Category_' ,category, sep="")
  team[category] <- as.numeric(2)
  
return(team)
  
}
```


```{r}
summarize_function(team_selection, race_category)
```

GENETIC ALGORITHM
```{r}
# GA using ensemble to build ensemble 
# Make evaluate function
evaluate <- function (x) {
  
  team <- summarize_function(x,race_category) # from driver selection, create team scores
  
  if(!any(is.na(team))){ # When input is all zero (no riders) immediately return low number, otherwise RF will throw error as the summarize_function will return an Na's which RF cannot handle
  
  # predict
  predlr <- predict(logreg, newx = data.matrix(team),
                  type = "response", s = 0.0003)
  predNB <- predict(NB, team, type = "raw", threshold = 0.001)[,2]
  predrF <- predict(rFmodel, team, type = "prob")[, 2]
  predAB <- predict(ABmodel, team)$prob[, 2]
  predlgbm <- predict(lgbm_model, as.matrix(team))
  predRoF <- predict(RoF, team)
  predxgb <- predict(xgb, xgb.DMatrix(as.matrix(team)))

  # combine predictions using AUC
  obj <- (auc_lr/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlr +
  (auc_nb/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predNB +
  (auc_rf/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predrF +
  (auc_ab/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predAB +
  (auc_lgbm/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlgbm +
  (auc_rof/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predRoF +
  (auc_xgb/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predxgb

  team_size = sum(x) 

  
  if((team_size > 7) || (obj<0) || (obj>1)) {
    return(0) # If you violate the constraint = return a very low number
  } else {
    return (obj) # Maximization by default
  }
  } else{
    return(0)
  }
}

#Model GA
# popsize and maxiter very low to avoid time out error
result <- ga(type = "binary",
               fitness = evaluate, 
               popSize = 50, 
               maxiter = 20, 
               pmutation = 0.1, 
               monitor = FALSE,
             nBits = team_size_all,# team size of whole available team
             selection = gabin_rwSelection, 
             suggestions = good_initial) 

summary(result)
```

```{r}
# Get selected drivers 
rider_selection <- summary(result)$solution[1,] %>% as.numeric()
rider_selection
```

```{r}
# Show solution
team_all[rider_selection == 1,]
```


PSO: population based, but should be faster (simple vector sum) than GA + higher level of randomization due to inertia 
Unfortunately, we can't make it work for binary DV...
```{r}
# evaluate_pso <- function (x) {
#   
#   team <- summarize_function(x,race_category) # from driver selection, create team scores
#   
#   if(!any(is.na(team))){ # When input is all zero (no riders) immediately return low number, otherwise RF will throw error as the summarize_function will return an Na's which RF cannot handle
#   
#    # predict
#   predlr <- predict(logreg, newx = data.matrix(team),
#                   type = "response", s = 0.0003)
#   predNB <- predict(NB, team, type = "raw", threshold = 0.001)[,2]
#   predrF <- predict(rFmodel, team, type = "prob")[, 2]
#   predAB <- predict(ABmodel, team)$prob[, 2]
#   predlgbm <- predict(lgbm_model, as.matrix(team))
#   predRoF <- predict(RoF, team)
#   predxgb <- predict(xgb, xgb.DMatrix(as.matrix(team)))
# 
#   # combine predictions using AUC
#   obj <- (auc_lr/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlr +
#   (auc_nb/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predNB +
#   (auc_rf/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predrF +
#   (auc_ab/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predAB +
#   (auc_lgbm/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlgbm +
#   (auc_rof/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predRoF +
#   (auc_xgb/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predxgb
#   
#   #constraints
#   team_size = sum(x) 
#   
#   
# 
#   
#   if((team_size > 7) || (!all(team %in% c(0,1))) ) {
#     return(1000000000000) # If you violate the constraint = return a very large number
#   } else {
#     return (-obj) # minimization by default
#   }
#   } else{
#     return(100000000000)
#   }
# }
# 
# #Model PSO
# # Parameters
# # maxit: the maximum number of iterations
# # maxf: the maximum number of function evaluations
# # abstol: the method converges once the best fitness obtained is less than or equal to abstol
# # reltol: the tolerance for restarting. Defaults to 0 which disables the check for restarting
# # s: the swarm size
# # k: The exponent for calculating number of informants. Defaults to 3 (nearest neighbors)
# # p: the average percentage of informants for each particle. Defaults to 1-(1-1/s)^k
# # w: the exploitation constant.  Defaults to 1/(2*log(2))
# 
# grid <- list(maxit = 20, maxf = Inf, 
#                  abstol = -Inf, reltol = 0, 
#                  s = 10, k = 3, p = 1 - (1 - 1/40)^3, 
#              w = 1/(2 * log(2)))
# 
# # PSO
# psoptim.results <- psoptim(par = team_selection,
#                            fn = evaluate_pso,
#                            lower = rep(0, team_size_all), 
#                            upper = rep(1, team_size_all), 
#                            control = list(maxit = grid$maxit, 
#                                           maxf = grid$maxf, 
#                                           abstol = grid$abstol, 
#                                           reltol = grid$reltol,
#                                           s = grid$s, 
#                                           k = grid$k, 
#                                           p = grid$p, 
#                                           w = grid$w))
# 
# psoptim.results$par

```
Binary pso function found online
Unfortunately it doesn't take into account the constraint...
```{r}
# # Binary pso function found on internet
# evaluate_Bpso <- function (x) {
#   
#   team <- summarize_function(x,race_category) # from driver selection, create team scores
#   
#   if(!any(is.na(team))){ # When input is all zero (no riders) immediately return low number, otherwise RF will throw error as the summarize_function will return an Na's which RF cannot handle
#   
#    # predict
#   # predlr <- predict(logreg, newx = data.matrix(team),
#   #                 type = "response", s = 0.0003)
#   # predNB <- predict(NB, team, type = "raw", threshold = 0.001)[,2]
#   # predrF <- predict(rFmodel, team, type = "prob")[, 2]
#   # predAB <- predict(ABmodel, team)$prob[, 2]
#   # predlgbm <- predict(lgbm_model, as.matrix(team))
#   # predRoF <- predict(RoF, team)
#   # predxgb <- predict(xgb, xgb.DMatrix(as.matrix(team)))
#   # 
#   # # combine predictions using AUC
#   # obj <- (auc_lr/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlr +
#   # (auc_nb/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predNB +
#   # (auc_rf/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predrF +
#   # (auc_ab/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predAB +
#   # (auc_lgbm/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlgbm +
#   # (auc_rof/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predRoF +
#   # (auc_xgb/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predxgb
#   
#   obj <- predict(rFmodel, team, type = "prob")[, 2]
#   
#   
#   #constraints
#   team_size = sum(x) 
#   
#   
# 
#   
#   if((team_size > 7) ) {
#     return(1000000000000) # If you violate the constraint = return a very large number
#   } else {
#     return (-obj) # minimization by default
#   }
#   } else{
#     return(100000000000)
#   }
# }
# #Model PSO
# results <- bpsoptim(par =team_selection, fn = evaluate_Bpso,
#                control = list(maxit = 100, s =40),
#                debug = TRUE)
# 
# 
# rider_selection <- results$par
# rider_selection
```

```{r}
# Get selected drivers 
# rider_selection <- summary(result)$solution[1,] %>% as.numeric()
# rider_selection
```

```{r}
# Show solution
# team_all[rider_selection == 1,]
```




Tabu Search
Unfortunalty we can't make it work for binary DV... 
```{r}
# BinaryVectorToReal <- function(y) {
#   .binary <- function(x,mb=max(.maxBit(x,g)),g=2) {
#     if( is.character(x) ) x<- .unbinary(x)
#     if( g==2 )
#       do.call(paste,c(sep="",lapply(mb:0,function(i) ifelse(.bit(x,i,g=2),"1","0"))))
#     else{
#       .toDigit <- function(x) c(0:9,LETTERS)[x+1]
#       do.call(paste,c(sep="",lapply(mb:0,function(i) .toDigit(.bit(x,i,g=g)))))
#     }
#   }
#   .unbinary <- function(x,g=2) {
#     if( is.numeric(x) )
#       return(x)
#     nc =nchar(x)
#     D = max(max(nchar(x)),2)
#     .asDigit <- (if(g==2) function(x) as.logical((match(x,c("0","1","F","T"))-1)%%2) else function(x) as.integer((match(x,as.character(c(0:9,LETTERS,10:19,letters)[c(1:g,37:(36+g))]))-1)%%g))
#     c(sapply(1:D,function(i) ifelse(i<=nc,.asDigit(substring(x,i,i))*g^(nc-i),rep(0,length(x))))%*%rep(1,D)) 
#   }
#   
#   .bit <- function(x,b,g=2) UseMethod(".bit")                       
#   .bit.numeric   <- function(x,b=0:.maxBit(x,g),g=2)  {
#     erg <- sapply(b,function(b) (x%/% (g^b) %% g ))
#     structure((if(g==2) as.logical else as.integer)(erg),dim=dim(erg))
#   }
#   .bit.character <- function(x,b=0:.maxBit(x,g),g=2)  {
#     nc = nchar(x)
#     .asDigit <- (if(g==2) function(x) as.logical((match(x,c("0","1","F","T"))-1)%%2) else function(x) as.integer((match(x,as.character(c(0:9,LETTERS,10:19,letters)[c(1:g,37:(36+g))]))-1)%%g))
#     erg <- sapply(b,function(b) ifelse(b<nc,substring(x,nc-b,nc-b),"0"))
#     structure(.asDigit(erg),dim=dim(erg))
#   }
#   
#   
#   .maxBit <- function(x,g=2) UseMethod(".maxBit")
#   .maxBit.numeric <- function(x,g=2) ceiling(log(x+1,g))-1
#   .maxBit.character <- function(x,g=2) max(nchar(x))-1
#   
#   ii = 0
#   y.paste <- as.character()
#   for (i in seq(0, (length(y) - 11), by = 11)) {
#     ii <- ii + 1
#     y.paste[ii] <- paste(y[(i + 1):(i + 11)], collapse = "")
#   }
#   real <- .unbinary(y.paste)
#   res <- real/sum(real)
#   res
# }
# 
# RealVectorToBinary <- function(x) {
#   .binary <- function(x,mb=max(.maxBit(x,g)),g=2) {
#     if( is.character(x) ) x<- .unbinary(x)
#     if( g==2 )
#       do.call(paste,c(sep="",lapply(mb:0,function(i) ifelse(.bit(x,i,g=2),"1","0"))))
#     else{
#       .toDigit <- function(x) c(0:9,LETTERS)[x+1]
#       do.call(paste,c(sep="",lapply(mb:0,function(i) .toDigit(.bit(x,i,g=g)))))
#     }
#   }
#   .unbinary <- function(x,g=2) {
#     if( is.numeric(x) )
#       return(x)
#     nc =nchar(x)
#     D = max(max(nchar(x)),2)
#     .asDigit <- (if(g==2) function(x) as.logical((match(x,c("0","1","F","T"))-1)%%2) else function(x) as.integer((match(x,as.character(c(0:9,LETTERS,10:19,letters)[c(1:g,37:(36+g))]))-1)%%g))
#     c(sapply(1:D,function(i) ifelse(i<=nc,.asDigit(substring(x,i,i))*g^(nc-i),rep(0,length(x))))%*%rep(1,D)) 
#   }
#   
#   .bit <- function(x,b,g=2) UseMethod(".bit")                       
#   .bit.numeric   <- function(x,b=0:.maxBit(x,g),g=2)  {
#     erg <- sapply(b,function(b) (x%/% (g^b) %% g ))
#     structure((if(g==2) as.logical else as.integer)(erg),dim=dim(erg))
#   }
#   .bit.character <- function(x,b=0:.maxBit(x,g),g=2)  {
#     nc = nchar(x)
#     .asDigit <- (if(g==2) function(x) as.logical((match(x,c("0","1","F","T"))-1)%%2) else function(x) as.integer((match(x,as.character(c(0:9,LETTERS,10:19,letters)[c(1:g,37:(36+g))]))-1)%%g))
#     erg <- sapply(b,function(b) ifelse(b<nc,substring(x,nc-b,nc-b),"0"))
#     structure(.asDigit(erg),dim=dim(erg))
#   }
#   
#   
#   .maxBit <- function(x,g=2) UseMethod(".maxBit")
#   .maxBit.numeric <- function(x,g=2) ceiling(log(x+1,g))-1
#   .maxBit.character <- function(x,g=2) max(nchar(x))-1
#   
#   x <- x * 100
#   y <- .binary(x, mb = 10)
#   y <- as.integer(unlist(strsplit(as.character(y), 
#                                     "")))
#   y
# }
```

```{r}
# # Function to evaluate (default is maximization)
# evaluateTabu <- function (x) {
#   x<-c(t(x))
#   team <- summarize_function(x,race_category) # from driver selection, create team scores
#   
#   if(!any(is.na(team))){ # When input is all zero (no riders) immediately return low number, otherwise RF will throw error as the summarize_function will return an Na's which RF cannot handle
#   
#   # predict
#   # predlr <- predict(logreg, newx = data.matrix(team),
#   #                 type = "response", s = 0.0003)
#   # predNB <- predict(NB, team, type = "raw", threshold = 0.001)[,2]
#   # predrF <- predict(rFmodel, team, type = "prob")[, 2]
#   # predAB <- predict(ABmodel, team)$prob[, 2]
#   # predlgbm <- predict(lgbm_model, as.matrix(team))
#   # predRoF <- predict(RoF, team)
#   # predxgb <- predict(xgb, xgb.DMatrix(as.matrix(team)))
#   # 
#   # # combine predictions using AUC
#   # obj <- (auc_lr/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlr +
#   # (auc_nb/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predNB +
#   # (auc_rf/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predrF +
#   # (auc_ab/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predAB +
#   # (auc_lgbm/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlgbm +
#   # (auc_rof/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predRoF +
#   # (auc_xgb/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predxgb
#   # 
#   obj <- predict(RoF, team)
#     
#   #constraints
#   team_size = sum(x) 
#   
#   
# 
#   
#   if((team_size > 7) ) {
#     return(0) # If you violate the constraint = return a very small number
#   } else {
#     return (obj) # max by default
#   }
#   } else{
#     return(0)
#   }
# }
# 
# # Function to evaluate (default is maximization)
# evaluateTabu2 <- function (x) {
#   
#   x <- as.integer(unlist(strsplit(as.character(x), "")))
#   x <- BinaryVectorToReal(y = x)
#     
#   team <- summarize_function(x,race_category) # from driver selection, create team scores
#   
#   if(!any(is.na(team))){ # When input is all zero (no riders) immediately return low number, otherwise RF will throw error as the summarize_function will return an Na's which RF cannot handle
#   
#   # predict
#   # predlr <- predict(logreg, newx = data.matrix(team),
#   #                 type = "response", s = 0.0003)
#   # predNB <- predict(NB, team, type = "raw", threshold = 0.001)[,2]
#   # predrF <- predict(rFmodel, team, type = "prob")[, 2]
#   # predAB <- predict(ABmodel, team)$prob[, 2]
#   # predlgbm <- predict(lgbm_model, as.matrix(team))
#   # predRoF <- predict(RoF, team)
#   # predxgb <- predict(xgb, xgb.DMatrix(as.matrix(team)))
#   # 
#   # # combine predictions using AUC
#   # obj <- (auc_lr/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlr +
#   # (auc_nb/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predNB +
#   # (auc_rf/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predrF +
#   # (auc_ab/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predAB +
#   # (auc_lgbm/(auc_lr + auc_nb + auc_rf + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predlgbm +
#   # (auc_rof/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predRoF +
#   # (auc_xgb/(auc_lr + auc_nb + auc_rf  + auc_ab + auc_lgbm + auc_rof + auc_xgb)) * predxgb
#   # 
#   obj <- predict(RoF, team)
#     
#   #constraints
#   team_size = sum(x) 
#   
#   
# 
#   
#   if((team_size > 7) ) {
#     return(0) # If you violate the constraint = return a very small number
#   } else {
#     return (obj) # max by default
#   }
#   } else{
#     return(0)
#   }
# }
# # Starting configuration
# performance <- rep(1/team_size_all, team_size_all)
# team_selection2 <- RealVectorToBinary(performance)
# BinaryVectorToReal(team_selection2)
# 
# # Parameters
# # iters : number of iterations
# # listSize: tabu list size
# grid <- list(iters = 2, listSize = c(5:12))
# 
# # tabuSearch
# tabu.results <- tabuSearch(size = length(team_selection2), 
#                            iters = grid$iters, 
#                            objFunc = evaluateTabu2,
#                            config = team_selection2)
# 
# rider_selection <- tabu.results$configKeep[which.max(tabu.results$eUtilityKeep), ]
# (rider_selection <- BinaryVectorToReal(y = rider_selection))
```

Also SA doesn't work for binary DV...
```{r}
# # Parameters
# # maxit: maximum number of iterations of the algorithm
# # temperature:  initial value for temperature
# # max.call: maximum number of call of the objective function (default is set to 1e7)
# # visiting.param: parameter for visiting distribution
# # acceptance.param: parameter for acceptance distribution
# grid <- list(maxit = 10, temperature = 0.5, 
#              max.call = 1e+07, visiting.param = 2.7, 
#              acceptance.param = -5)
# 
# evaluate_SA <- function (x) {
#   
#   team <- summarize_function(x,race_category) # from driver selection, create team scores
#   
#   if(!any(is.na(team))){ # When input is all zero (no riders) immediately return low number, otherwise RF will throw error as the summarize_function will return an Na's which RF cannot handle
#   
#   # predict
#   #predlr <- predict(logreg, newx = data.matrix(team),
#                   #type = "response", s = 0.0003)
#   p_load(randomForest, xgboost, glmnet, AUC, e1071, FNN, catboost, fastAdaboost, lightgbm, rotationForest)
#   predNB <- predict(NB, team, type = "raw", threshold = 0.001)[,2]
#   predrF <- predict(rFmodel, team, type = "prob")[, 2]  
#   predAB <- predict(ABmodel, team)$prob[, 2]  
#   predlgbm <- predict(lgbm_model, as.matrix(team))   
#   predRoF <- predict(RoF, team)  
#   predxgb <- predict(xgb, xgb.DMatrix(as.matrix(team)))  
#   
#   #obj <- (predAB + predrF + predNB)/3
#   obj <- (predNB+ predrF + predAB+ predlgbm+ predRoF+ predxgb)/6
#   team_size = sum(x) 
# 
#   
#   if(team_size > 7) {
#     return(0) # If you violate the constraint = return a very high number
#   } else {
#     return (-obj) # Minimization by default
#   }
#   } else{
#     return(0)
#   }
# }
# 
# # GenSA
# # par: initial values. Give equal weight to every algo to start
# # fn: the function to be optimized (the same as genalg)
# GenSA.results <- GenSA(par = c(0,0,0,0,1,0,0,1,1,0,0,0,0,0,0,0,1,0,1,0,1,0,0,1), 
#                        lower = rep(0, team_size_all), 
#                        upper = rep(1, team_size_all), 
#                        fn = evaluate_SA, 
#                        control = list(maxit = grid$maxit, 
#                                       temperature = grid$temperature, 
#                                       max.call = grid$max.call,
#                                       visiting.param = grid$visiting.param, 
#                                       acceptance.param = grid$acceptance.param,
#                                       verbose=TRUE))
# 
# 
# 
# # Get selected drivers 
# rider_selection <- GenSA.results$par
# rider_selection
# 
# # Show solution
# team_all[rider_selection == 1,]
```




